Convergence rate of MAP estimates \\ for the exponential family

### 2021-10-08 aistats.tex
some comments

% my packages
\usepackage{math_commands}
% some custom math commands
\newtheorem{proposition}{Proposition}
\newcommand*{\expect}[2][]{\ensuremath{\mathbb{E}_{#1} \left[ #2 \right] }} % expectation operator
\newcommand{\cond}{\,\vert\,}
\newcommand{\logpart}{A}
\newcommand{\conj}{\logpart^*}
\newcommand{\bregman}{\cB_\logpart}
\newcommand{\bregmanconj}{\cB_{\logpart^*}}
\newcommand{\nat}{\theta}
\newcommand{\m}{m}
\newcommand{\meanp}{\m}
\newcommand{\decrement}{D}
\newcommand{\linear}{\ell} % linearization of a function
\newcommand{\lr}{\gamma} % learning rate, or step-size
\newcommand{\lin}[1]{\left\langle#1\right\rangle}

@@

\subsection{Locally Quadratic Case}
All Bregman divergences are locally quadratic. 
Under some assumptions, we can quantify  when this quadratic behavior  kicks in.
For instance {\bf when $\conj$ is self-concordant} \citep[Ch.4.1]{nesterov2003introductory}. 
This is true when $T$ is 1-dimensional and $\logpart$ is self-concordant 
-- e.g. exponential distribution, 
Gaussian and Laplace distributions with known mean,
Pareto distribution with known minimum value, 
Weibull distribution with known shape k
-- or when $T$ lives in a compact \citep{bubeck2015entropic}. Then the bound
\begin{align}
	 \bregmanconj(\m^*,\m) \leq \norm{\m^*-\m}_{\mF^*}^2
\end{align}
holds whenever $\norm{\m^*-\m}_{\mF^*} < 0.21$. 
Similarly, \citet{kakade2010learning} assumes a bound on all higher order moments at $\nat^*$ to quantify when $\logpart$ starts behaving quadratically, but their rate does not directly apply to $\conj$ and $\m$.

@@

\subsection{Bias-Variance Decomposition}
In both examples (add link), the upper bound takes the form $O(\inv{n}) + O(\frac{\text{bias}}{n^2})$, reminding us of the bias-variance decomposition. In fact, it is possible to write such a decomposition for any Bregman divergence
Let $\tilde \theta_n := \expect{\hat \theta_n}$ be the expectation of the MAP in primal space, and $\tilde \m_n = \nabla \logpart(\tilde \theta_n )$ be the corresponding mean parameter.
As described by \citet[Theorem 0.1]{pfau2013generalized}, the  expected Bregman decomposes like
\begin{align}
	\expect{\bregmanconj(\m^* ; \hat \m_n)} 
	&= {\bregmanconj(\m^* ; \tilde \m_n)}
	+ {\expect{\bregmanconj(\tilde \m_n ; \MAPm)}}
	\label{eq:primal_pivot}
\end{align}

>>>>

% my packages
\usepackage{math_commands}
% some custom math commands
\newtheorem{proposition}{Proposition}
\newcommand*{\expect}[2][]{\ensuremath{\mathbb{E}_{#1} \left[ #2 \right] }} % expectation operator
\usepackage{suffix}
\WithSuffix\newcommand\expect*[2][]{\ensuremath{\mathbb{E}_{#1} [ #2 ] }} % expectation operator

\newcommand{\cond}{\,\vert\,}
\newcommand{\logpart}{A}
\newcommand{\conj}{\logpart^*}
\newcommand{\bregman}{\cB_\logpart}
\newcommand{\bregmanconj}{\cB_{\logpart^*}}
\newcommand{\nat}{\theta}
\newcommand{\m}{m}
\newcommand{\meanp}{\m}
\newcommand{\decrement}{D}
\newcommand{\linear}{\ell} % linearization of a function
\newcommand{\lr}{\gamma} % learning rate, or step-size
\newcommand{\lin}[1]{\left\langle#1\right\rangle}

@@

\subsection{Locally Quadratic Case}
All Bregman divergences are locally quadratic. 
Under some assumptions, we can quantify  when this quadratic behavior  kicks in.
For instance {\bf when $\conj$ is self-concordant} \citep[Ch.4.1]{nesterov2003introductory}. 
This is true when $T$ is 1-dimensional and $\logpart$ is self-concordant 
-- e.g. exponential distribution, 
Gaussian\fdk{with known variance?} and Laplace distributions with known mean,
Pareto distribution with known minimum value, 
Weibull distribution with known shape $k$
-- or when $T$ lives in a compact \citep{bubeck2015entropic}. Then the bound
\begin{align}
	 \bregmanconj(\m^*,\m) \leq \norm{\m^*-\m}_{\mF^*}^2
\end{align}
holds whenever $\norm{\m^*-\m}_{\mF^*} < 0.21$.\fdk{where does this $0.21$ come from?}
Similarly, \citet{kakade2010learning} assumes a bound on all higher order moments at $\nat^*$ to quantify when $\logpart$ starts behaving quadratically, but their rate does not directly apply to $\conj$ and $\m$.

@@

\subsection{Bias-Variance Decomposition}
In both examples (add link), the upper bound takes the form $O(\inv{n}) + O(\frac{\text{bias}}{n^2})$, reminding us of the bias-variance decomposition. In fact, it is possible to write such a decomposition for any Bregman divergence
Let $\tilde \theta_n := \expect*{\hat \theta_n}$ be the expectation of the MAP in primal space, and $\tilde \m_n = \nabla \logpart(\tilde \theta_n )$ be the corresponding mean parameter.
As described by \citet[Theorem 0.1]{pfau2013generalized}, the  expected Bregman decomposes like
\begin{align}
	\expect{\bregmanconj(\m^* ; \hat \m_n)} 
	&= {\bregmanconj(\m^* ; \tilde \m_n)}
	+ {\expect{\bregmanconj(\tilde \m_n ; \MAPm)}}
	\label{eq:primal_pivot}
\end{align}
